Matching bullets

### 2015-11-21 imaging-paper.Rnw
Add scales as a dependency

<<fixedX, dependson='data', echo=FALSE, warning=FALSE, message=FALSE, fig.height=2.5, fig.width=6, out.width='\\linewidth', fig.pos='t!', fig.cap='Side profile of the height values of a bullet land across fixed x values. Note that the global features dominate any deviations, which would correspond to markings.'>>=
library(RColorBrewer)
library(ggplot2)
library(dplyr)
library(x3pr)
library(x3prplus)

>>>>

<<fixedX, dependson='data', echo=FALSE, warning=FALSE, message=FALSE, fig.height=2.5, fig.width=6, out.width='\\linewidth', fig.pos='t!', fig.cap='Side profile of the height values of a bullet land across fixed x values. Note that the global features dominate any deviations, which would correspond to markings.'>>=
library(RColorBrewer)
library(ggplot2)
library(scales)
library(dplyr)
library(x3pr)
library(x3prplus)
